### 2018-11-21 zst/data/reference.tex
update

>>>>

\bibitem{ss-46}
Gilson C , Hietarinta J , Nimmo J , et al. The Sasa-Satsuma higher order nonlinear Schrodinger equation and its bilinearization and multi-soliton solutions[J]. Physical Review E Statistical Nonlinear \& Soft Matter Physics, 2003, 68(2):016614.

\bibitem{ss-45}
Liu Y , Gao Y T , Xu T , et al. Soliton Solution, Bäcklund Transformation, and Conservation Laws for the Sasa-Satsuma Equation in the Optical Fiber Communications[J]. Zeitschrift Für Naturforschung A, 2010, 65(4):291-300.

\bibitem{ss-40}
Chen S . Twisted rogue-wave pairs in the Sasa-Satsuma equation[J]. Phys Rev E Stat Nonlin Soft Matter Phys, 2013, 88(2):023202.

\bibitem{ss-39}
Mu G , Qin Z . Dynamic patterns of high-order rogue waves for Sasa–Satsuma equation[J]. Nonlinear Analysis Real World Applications, 2016, 31:179-209.
